Predicting Conflict Escalation

### 2023-04-30 docs/hes_final/article.qmd
update test prediction map figures

![Predictions for 2023-01 from transformer model](imgs/fig-y_pred_proba-transformer-202301.png){width=50%}

![Predictions for 2023-01 from xgboost model](imgs/fig-y_pred_proba-xgboost-202301.png){width=50%}

![Predictions for 2023-01 from ffnn model](imgs/fig-y_pred_proba-ffnn-202301.png){width=50%}

>>>>

![Transformer model Predictions on test data](imgs/fig-transformer-test-predictions.png){width=55%}

![XGBoost model predictions on test data](imgs/fig-xgboost-test-predictions.png){width=55%}

![FFNN model predictions on test data](imgs/fig-ffnn-test-predictions.png){width=55%}
